### 2022-09-06 main/chapter_searches.tex
minor tweaks on likelihoods and p-values

But $B: t \geq \tilde{t}$ is a logical statement (true for all test statistics
greater than or equal to the observed value) and not a randomly occurring
event, so its assignment frequentist probability is deeply dubious.
Much more importantly, the reduction to a one-sided inequality has no tangible
benefit; it reduces the information content of the reported data, but does not
reduce the costs of reporting or interpreting those data.
Both $A$ and $B$ are printed in the same number of characters, and $p$-values
can be painfully expensive to evaluate.
Furthermore, it actively harms any result with small a test statistic by
diluting the likelihood ratio, since if
\begin{equation}
\log \frac{L(h_1)}{L(h_2)}
\to
\log \frac{
L(h_1) + \prob{t > \tilde{t}}{h_1}
}
{
L(h_2) + \prob{t > \tilde{t}}{h_2}
}
\end{equation}
then large tail probabilities will only squash the $\log$ likelihood ratio
toward zero.

@@

Fisher claims that the $p$-value indicates the ``significance'' of an
observation~\cite{fisher1925smrw}, with small or large values being
suspiciously significant, and that
``If $P$ is between $.1$ and $.9$ there is certainly no reason to suspect the
hypothesis tested.''~\cite{fisher1925smrw}
This may have been true for his intended applications, but it is not general.

>>>>

But $B: t \geq \tilde{t}$ is a logical statement (true for all test statistics
greater than or equal to the observed value) and not a randomly occurring
event, so its assignment frequentist probability is deeply dubious.
Much more importantly, the reduction to a one-sided inequality has no tangible
benefit; it reduces the information content of the reported data, but does not
reduce the costs of reporting or interpreting those data.
Both $A$ and $B$ are printed in the same number of characters, and $p$-values
can be painfully expensive to evaluate.
Furthermore, it actively harms any result with small a test statistic by
diluting the likelihood ratio, since if
\begin{equation}
\log \frac{L(h_1)}{L(h_2)}
\to
\log \frac{
L(h_1) + \prob{t > \tilde{t}}{h_1}
}
{
L(h_2) + \prob{t > \tilde{t}}{h_2}
}
\end{equation}
then large tail probabilities squash the $\log$ likelihood ratio toward zero.

@@

Fisher claims that the $p$-value indicates the ``significance'' of an
observation~\cite{fisher1925smrw}, with small or large values being
suspiciously significant, and that
``If $P$ is between $.1$ and $.9$ there is certainly no reason to suspect the
hypothesis tested.''~\cite{fisher1925smrw}
This may have been true for his intended applications, but it is not general;
as for usual likelihood functions, small values are only meaningful in
comparison against larger values.
